SSA based global code motion of identical computations

### 2017-04-16 acmart-pacmpl-template.tex
overall algorithm

>>>>

% Explain the overall algorithm, explain how anticipability is computed on demand
% explain the pinned-instructions/barriers.
\begin{verbatim}
Analyses available: Dominator Tree, DFS Numbering, Memory SSA,

Compute GVN of each expression in the function
Compute DJ Graph of function and compute mergeset based on that

For each value number VN with 2 or more instructions:
  sort the instructions according to DFSIn numbers
  if first two I1, I2 are hoistable:
    if they are anticipable at hoist-point:
      if they are profitable to be hoisted at hoist-point:
        proceed to check hoistability of subsequent instruction with same VN
      else
        proceed to check if I2 and I3 (if available) is hoistable

For each hoistable VN:
  move the first one I1 to the hoist-point
  update the use of all other candidates to refer to I1
  remove all others.
  if I1 has memory references (a load, store etc.)
    update MemorySSA of I1 and others to point to the MemorySSA reference of I1
    remove MemorySSA reference of all others which were deleted
  update statistics

If any of candidates were hoisted then repeat hoisting
Once no more candidates are hoistable proceed to sinking
\end{verbatim}

\begin{verbatim}
Analyses available: Dominator Tree, DFS Numbering, Memory SSA, Mergeset
Compute GVN of each expression in the function

For each value number VN with 2 or more instructions:
  if there are two instructions with same immediate successor as post-dominator
    if both are only used in the same PHI-node of the successor
      if both have dependencies that are available or can be made available at the sink point
         mark VN as sinkable

For each pair I1, I2 of sinkable instructions:
  Move the first one I1 to the sink point which is just after all the PHI-nodes
  in the post-dominator
  update the use of PHI with I1
  Remove I2 and PHI
  if I1 is a memory reference:
    update MemorySSA of I1 and others to point to the MemorySSA reference of I1
    remove MemorySSA reference of all others which were deleted
  update statistics
